\documentclass[a4paper, 12pt]{article}

\input{preamble}

\begin{document}
% This sets the default language for the listings package.
\lstset{language=Python}
\title{
\sffamily
{\huge\textbf{Report on Project 1}} \\
Cosmological Models
}
\author{
    \begin{minipage}[t]{0.45\textwidth}
\centering
Linus Brink\\
\href{mailto:brinkl@chalmers.se}{brinkl@chalmers.se}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.45\textwidth}
\centering
Oscar Stommendal\\
\href{mailto:oscarsto@chalmers.se}{oscarsto@chalmers.se}
\end{minipage}
}
\date{\today}
\maketitle
This is a course on \textit{Advanced Simulation and Machine Learning}. Although it
is a physics course, it has an obvious focus on statistics, i.e., inference,
optimization, parameter estimation, etc. It is therefore important that you discuss
your findings and demonstrate your ability to use appropriate terminology to
describe the employed statistical, analytical, and computational methodologies.\\
Please refer to the respective project documents for additional instructions.
\section{Some recommendations}
You can use this document as a starting point for your report.
It has been sensibly (from our perspective) configured and demonstrates some
potentially useful packages.
\subsection{Abbreviations}
We recommend using the \texttt{glossaries} package for handling abbreviations.
It will take care of making sure an abbreviation is introduced on its first
occasion in the text.
For example, the \gls{rmse} is ridiculously low but only if the \gls{rmse} is less
than two elephants.
\subsection{Units}
We recommend using the \texttt{siunitx} package for handling units.
For example, the Suez Canal measures \SI{193.3}{\kilo\meter}, a value that has been
vetted by the scrupulous editors of Wikipedia.
Believe it or not but the speed limit for scooters is \SI{20}{\kilo\meter\per\hour}
according to \href{https://scotsman.me/post/what-s-the-law-on-riding-a-scooter-in-
sweden}{this webpage}.
Sometimes you might also just want to denote a unit in its full glory, such as
\si{\nano\meter\squared}.
\section{General instructions}
The following points are based on the experience in previous years.
We assume that all of you are familiar with these aspects but it is useful to keep
them in mind when writing the reports.
\subsection{Units}
\begin{itemize}
\item
All numbers must be reported with proper units.
\item
Please note that if you choose to standardize the target data (e.g., the mixing
energies that are originally in \si{\milli\electronvolt\per\atom} in project 2a)
this unit changes upon standardization.
This must be corrected for afterwards to obtain a \gls{rmse} that can be
compared to the original data in a meaningful way.
\item
Check your units and target data.
If the \gls{mse} is of the order of the variance of the target data, the model
is not better than guessing.
It is strongly recommended to use the same units as the data.
\end{itemize}
\subsection{Simulations in general}
\begin{itemize}
\item
Clearly state how you choose your parameters.
\end{itemize}
\subsection{\texorpdfstring{\gls{mcmc}}{MCMC} simulations}
A careful \gls{mcmc} simulation should contain the following for each class of
parameters (model parameters and hyper-parameters):
\begin{itemize}
\item
An illustration of the burn-in to motivate how much of the initial data to
throw away.
\item
How the walkers were initialized.
\item
Some measure of the decoherence length (here the chain itself can be used but
preferably an auto-correlation plot should be made).
\item
Some motivation of a successful total sampling, e.g., a histogram (it should at
least be rather 'smooth') can be used for each parameter class.
The \href{https://corner.readthedocs.io/}{\texttt{corner} package} can be a
real boon for such tasks.
\end{itemize}
\subsection{Bayesian data analysis}
\begin{itemize}
\item
Priors must be clearly stated, motivated and optionally illustrated in a
figure.
\item
Motivate and declare your likelihood function. What are the statistical grounds
for it?
\item
It is useful plot the posteriors.
This can help you spot errors. A \texttt{corner} plot of the posterior is often
useful to include in the report.
\item Motivate your physical model/theory.
\end{itemize}
\subsection{Tables}
\begin{itemize}
\item
Tables are useful for reporting/contrasting
results.
\end{itemize}
\subsection{Figures}
\begin{itemize}
\item
Figures must be reported in the correct units and have proper axis labels.
It is insufficient to simply write ``RMSE'', ``CV'' etc.
\item
Please make sure that your figure are in sufficiently high resolution.
Also keep in mind that if PDF is a vector format.
This implies that if you generate a figure with a lot of dots (or other
symbols) all these data survive even if the symbols overlap (as they typically do
for example in a parity plot).
In such a case, PDF files can become very large and unwieldy.
Under such circumstances, a bitmap format, preferably PNG, is preferable if you
make sure that the resolution is still sufficiently high.
\end{itemize}
\end{document}